---
output:
  github_document:
knitr:
  opts_chunk:
    fig.path: "figures/"
---
```{r, include = FALSE}
library(knitr)
```
# Kinship Analysis

## Tools & manuals  
*vcftools* v0.1.16 [manual.](https://vcftools.github.io/man_latest.html)  

## Kinship dataset

### Removal of unrelated individuals  
Individuals that were found to genetically differ from the majority in the Palmer Archipelago were excluded from the kinship dataset. This was determined using structure and a PCA.  

Firstly, a list of individuals to exclude from the entire dataset was created, and saved as a text file: ```KINSHIP_remove.txt```.   
```
Individuals removed: 
RN02_L0107
RN02_L0108
RN02_L0120
RN02_L0124
RN02_L0131
RN02_L0137
RN02_L0138
RN02_L0147
RN02_L0153
RN02_L0126
RN02_L0130
RN02_L0132
RN02_L0133
RN02_L0134
RN02_L0135
RN02_L0136
RN02_L0125
RN02_L0127
RN02_L0146
RN02_L0149
RN02_L0150
RN02_L0152
RN02_L0154
RN02_L0156
RN02_L0157
RN02_L0032
RN02_L0033
RN02_L0035
RN02_L0039
RN02_L0040
RN02_L0041
RN02_L0043
RN02_L0045
RN02_L0047
RN02_L0050
RN02_L0053
RN02_L0054
RN02_L0060
RN02_L0061
RN02_L0163
RN02_L0164
RN02_L0067
RN02_L0056
RN02_L0062
RN02_L0139
RN02_L0141
RN02_L0142
RN02_L0145
RN02_L0148
RN02_L0158
RN02_L0160
```
```
vcftools --vcf site_depth.recode.vcf --remove KINSHIP_remove.txt --recode --recode-INFO-all --out KINSHIP_initial
```

As this kinship dataset comprised a new configuration of individuals, population specific SNP filtering was applied.  


After filtering, kept 73736 out of a possible 73736 Sites.

### Remove sites by missingness  

Site missingness was calculated using vcftools v0.1.16 functions --keep and --missing-site.

```
vcftools --vcf KINSHIP_initial.recode.vcf --max-missing 1.0 --recode --recode-INFO-all --out KINSHIP_maxmissing
```  

After filtering, kept 72236 out of a possible 73736 Sites.

### Filter by maximum observed heterozygosity  
Heterozygosity for a biallelic SNP should theoretically be ≤0.5. Values > 0.5 may represent paralogous loci or multilocus contigs (ref: https://onlinelibrary.wiley.com/doi/full/10.1111/j.1755-0998.2010.02967.x). Therefore, sites with an observed heterozygosity >0.5 were found and removed. This was done in R, using the packages ```adegenet``` and ```vcfr```. 

```
Required R packages:  
#install.packages("adegenet")
#install.packages("vcfR")
library(adegenet)
library(vcfR)

#calculating site heterozygosity for fine scale dispersal data  

#import vcf file into R
vcf_kinship <- read.vcfR("KINSHIP_CR1.recode.vcf")
#convert vcf data into a genind object
kinship_genind <- vcfR2genind(vcf_kinship)
#summary statistics
summary_kinship = summary(kinship_genind)
summary_kinship$Hobs
#export site heterozygosity into a csv file
write.csv(summary_kinship$Hobs, file = "kinship_Hobs_per_SNP.csv")
```  

Sites with a heterozygosity ≥ 0.7 can now be removed.  

```
vcftools --vcf KINSHIP_maxmissing.recode.vcf --exclude-positions Het_remove.txt --recode --recode-INFO-all --out KINSHIP_max_het
```

After filtering, kept 64089 out of a possible 72236 Sites.

### Filter by MAF  
```
vcftools --vcf KINSHIP_max_het.recode.vcf --maf 0.05 --recode --recode-INFO-all --out KINSHIP_maf0.05
```  
After filtering, kept 11576 out of a possible 64089 Sites.

### Select one SNP per locus
```
vcftools --vcf KINSHIP_maf0.05.recode.vcf --thin 500 --recode --recode-INFO-all --out KINSHIP_SNPs
```  
After filtering, kept 4341 out of a possible 11576 Sites.

##Kinship Analysis  

###Colony

###Sequoia

First the VCF file will be converted into a .RAW file that can be interpreted by Sequoia. 

```
#convert vcf file to plink
#plink --vcf KINSHIP_SNPs.recode.vcf --allow-extra-chr --recode --out KINSHIP_SNPs
#extract data from plink file
#plink --file KINSHIP_SNPs --allow-extra-chr --recodeA --out sequoia_KINSHIP_SNPs
```  

Sequoia was then run 

###MCMC-ped

I need to transfrom my .vcf file into .tped format. This can be done with plink.

```
plink --vcf KINSHIP_SNPs.recode.vcf --allow-extra-chr --make-bed --out MCMC_KINSHIP_BINARY
plink --bfile MCMC_KINSHIP_BINARY --allow-extra-chr --recode transpose --out MCMC_KINSHIP
```

Recode column 3 and 4 to 0 as genetic distance and physical distance is both unknown for ddRADseq data.

```
awk '{$3 = 0; $4 = 0; OFS=" "; print}' input.tped > output.tped
```

###Related R Package

Firstly, a genotype file needs to be created. It is similar to the format structure uses, so it will be formatted that way.

```
plink --vcf KINSHIP_SNPs.recode.vcf --allow-extra-chr --recode --out kinshiptemp
plink --file kinshiptemp --allow-extra-chr --recode structure --out KINSHIP_related
```

###Pairwise relatedness with plink
Pairwise relatedness will be calculated with dataset2, as it relies on population allele frequencies. Dataset2 includes samples outside of the PAL which are identified to be part of the same population with structure analyses.

```
plink --vcf KINSHIP_SNPs.recode.vcf --allow-extra-chr --make-bed --out KINSHIP_bed
plink --bfile KINSHIP_bed --allow-extra-chr --genome --out KINSHIP_plink
```

The .genome file produced by plink can then be analysed in R to calculate a kinship coefficient. 

```
ibd_probabiliteis <- read.table("KINSHIP_plink.genome", header = TRUE)
kinship_coefficient = ibd_probabiliteis$Z1/4+ibd_probabiliteis$Z2/2
ibd_probabiliteis$kinship_coefficient = kinship_coefficient
```

###Coancestry

*Simulated dataset*

First a simulated dataset will be created to determine the best estimator. To be consistent,
allele frequencies will be generated with plink.

```
plink --bfile KINSHIP_bed --allow-extra-chr --freq --out KINSHIP_allele_freqs

In R:
# Read PLINK .frq file
frq <- read.table("KINSHIP_allele_freqs.frq", header = TRUE)


# Define allele to integer mapping
allele_map <- c("A" = 1, "T" = 2, "C" = 3, "G" = 4)

# Map A1 and A2 to integers
frq$A1_code <- allele_map[as.character(frq$A1)]
frq$A2_code <- allele_map[as.character(frq$A2)]

# Construct lines for COANCESTRY
allele_lines <- paste(frq$A1_code, frq$A2_code)
freq_lines <- paste(frq$MAF, 1 - frq$MAF)

# Interleave allele and frequency lines
output <- character(length(freq_lines) * 2)
output[seq(1, length(output), 2)] <- allele_lines
output[seq(2, length(output), 2)] <- freq_lines

# Write to file
writeLines(output, "coancestry_allele_freqs.txt")

```

A text file containing loci missing rate, error rate and allelic dropout was then generated.

```
#Set number of loci
n_loci <- 4341

#Create a data frame
loci_error_rates <- data.frame(
  MissingRate = rep(0, n_loci),
  GenotypingError = rep(0.01, n_loci),
  AllelicDropout = rep(0.01, n_loci)
)

#Write to space-delimited text file with no header
write.table(loci_error_rates, "coancestry_locus_error_rates.txt", 
            row.names = FALSE, col.names = FALSE, quote = FALSE)
```

Next, true relatedness to be simulated was determined. This included 500 of each: parent/offspring pairs, full siblings, half siblings, first cousins and unrelated pairs. For information regarding 
identity by descent coefficients , see [Wang, 2007](https://doi.org/10.1017/s0016672307008798).

```{r,echo = FALSE}
data_frame <- data.frame(
  Relationship = c("PO","FS","HS","1C","UR"),
  S7 = c(0, 0.25, 0, 0, 0),
  S8 = c(1, 0.5, 0.5, 0.25, 0),
  S9 = c(0, 0.25, 0.5, 0.75, 1)
  
)
kable(data_frame, caption = "Table 1: Identity by descent coefficients for simulated kinship dyads.")
```

###Empirical data

```
plink --bfile KINSHIP_bed --allow-extra-chr --recode --out KINSHIP_coancestry_tmp
cut -f2,7- KINSHIP_coancestry_tmp.ped > coancestry_genotypes.txt
```